Are mental properties supervenient on brain properties?

### 2011-08-10 nature_sci_rep/submission2/supervenience.tex
explained that super need not be crazy hard or eps crazy small

In this work we attempt to bridge the gap between philosophical conjecture and empirical investigations by casting supervenience in a probabilistic framework amenable to hypothesis testing. 
We then use the probabilistic theory of pattern recognition to determine
 % This perspective leads to a greater understanding vis-\'a-vis 
the limits of what one can and cannot learn about supervenience through data analysis.

@@

Interestingly, much of contemporary research in neuroscience and cognitive science could be cast as mind-brain supervenience investigations.  Specifically, searches for ``engrams'' of  memory traces \cite{Lashley50} or ``neural correlates''  of various behaviors or mental properties (for example, consciousness \cite{Koch2010}), may be more aptly called searches for the ``neural supervenia'' of such properties.
% any investigation that aims to ``explain'' some behavioral or psychological phenomenon by reference to neural (or other brain) activity or structure could be thought of as mind-brain supervenience investigations.  
% Thus, the proposed $\eps$-supervenience framework is perhaps a useful unifying perspective.
 % for these fields.  
% The above Gedankenexperiment is an 
Letting the brain property be a brain-graph is perhaps especially pertinent in light of the advent of ``connectomics'' \cite{SpornsKotter05,Hagmann05}, a field devoted to estimating whole organism brain-graphs and relating them to function.  Testing supervenience of various mental properties on these brain-graphs will perhaps therefore become increasingly compelling; the framework developed herein could be fundamental to these investigations.  
% Note that these connectomics investigations might lack any dynamics; rather, they effectively assume that structure determines the relevant dynamics.  Assuming that dynamics are a function of either vertex or edge attributes, whether any particular mental property is supervenient to ``only'' connectivity structure, or also some attributes, is merely another $\eps$-supervenience hypothesis. 
For example, questions about whether connectivity structure alone is sufficient to explain a particular mental property is one possible mind-brain $\eps$-supervenience investigation.  The above synthetic data analysis demonstrates the feasibility of $\eps$-supervenience on small brain-graphs.
% Appendix 2 presents an illustrative simulated example using the only currently known connectome---that of a Caenorhabditis elegans---demonstrating that $\eps$-supervenience can be rejected at some critical value $c_\alpha$ with only a reasonably small number of samples. 
Similar supervenience tests on larger animals (such as humans) will potentially benefit from either higher-throughput imaging modalities \cite{HayworthLichtman06, Bock2011}, more coarse brain-graphs \cite{PalmAmunts10,Johansen-Berg2009}, or both.

>>>>

In this work we attempt to bridge the gap between philosophical conjecture and empirical investigations by casting supervenience in a probabilistic framework amenable to hypothesis testing. 
We then use the probabilistic theory of pattern recognition to determine
the limits of what one can and cannot learn about supervenience through data analysis.  
The implications of this work are varied.  It provides a probabilistic framework for converting philosophical conjectures into statistical hypotheses that are amenable experimental investigation, which  allows the philosopher to gain empirical support for her rational arguments. This leads to the construction of the first explicit proof (to our knowledge) of a universally consistent classifier on graphs, and the first demonstration of the tractability of answering supervenience questions.  Supervenience therefore seems to perhaps be a useful (but under utilized) concept for neuroscientific investigations.  This should provide further motivation for cross-disciplinary efforts across three fields---philosophy, statistics, and neuroscience---with shared goals but mostly disjoint jargon and methods of analysis.

@@

Interestingly, much of contemporary research in neuroscience and cognitive science could be cast as mind-brain supervenience investigations.  Specifically, searches for ``engrams'' of  memory traces \cite{Lashley50} or ``neural correlates''  of various behaviors or mental properties (for example, consciousness \cite{Koch2010}), may be more aptly called searches for the ``neural supervenia'' of such properties.
Letting the brain property be a brain-graph is perhaps especially pertinent in light of the advent of ``connectomics'' \cite{SpornsKotter05,Hagmann05}, a field devoted to estimating whole organism brain-graphs and relating them to function.  Testing supervenience of various mental properties on these brain-graphs will perhaps therefore become increasingly compelling; the framework developed herein could be fundamental to these investigations.  
For example, questions about whether connectivity structure alone is sufficient to explain a particular mental property is one possible mind-brain $\eps$-supervenience investigation.  The above synthetic data analysis demonstrates the feasibility of $\eps$-supervenience on small brain-graphs.
Note that $\eps$-supervenience tests need not investigate seemingly intractable problems, like consciousness.  For example, it already seems quite clear that visual perception supervenes on visual cortical activity \cite{??}. Moreover, an inability to reject $\eps$-supervenience for small $\eps$ is also potentially meaningful.  For example, perhaps auditory localization precision supervenes on a rate code only to some $\eps > c$, the rest supervening on a spike timing code \cite{??}. 
Similar supervenience tests on increasingly complex mental properties will potentially benefit from either higher-throughput imaging modalities \cite{HayworthLichtman06, Bock2011}, more coarse brain-graphs \cite{PalmAmunts10,Johansen-Berg2009}, or both.
